Behavior Driven Development in Haskell

### 2012-05-28 paper.tex
clearly say that we implemented Doctest in Haskell.
adding CI ref and describe monad low.

%%%% Describe the problem.
\begin{quote}
    TBD: Important points we want to say about BDD:
    \begin{itemize}
        \item
            All behavior should be documented, together with some
            \emph{evidence} for that behavior.
        \item
            \emph{Behavior driven development (BDD)} approaches
            \emph{test-driven development (TDD)} and \emph{acceptance
            test-driven development (ATDD)} with a new terminology and
            mindset.  For the purpose of this paper we only focus on
            the TDD aspect of BDD.
        \item
            Automating things, and continuous integration is an important
            aspect of BDD.
        \item
            BDD uses expectations instead of assertions
    \end{itemize}
\end{quote}

@@

Unfortunately, the type system of Haskell does not always guarantee
correct semantics.

\begin{quote}
    TBD: Make it plausible, that the type system does not always
    guarantee correctly semantics.
    \begin{itemize}
        \item Many of the standard type classes \emph{should} adhere
            to certain laws.
        \item The type system does not enforce those laws.
        \item It is the programmers responsibility to ensure that
            instance definitions \emph{behave} as \emph{expected}.
    \end{itemize}
\end{quote}

@@

\begin{itemize}
\item
    Add support for QuickCheck properties to Doctest (Section
    \ref{sec:for-users} and Section \ref{sec:doctest})

>>>>

%%%% Describe the problem.
\begin{quote}
    TBD: Important points we want to say about BDD:
    \begin{itemize}
        \item
            All behavior should be documented, together with some
            \emph{evidence} for that behavior.
        \item
            \emph{Behavior driven development (BDD)} approaches
            \emph{test-driven development (TDD)} and \emph{acceptance
            test-driven development (ATDD)} with a new terminology and
            mindset.  For the purpose of this paper we only focus on
            the TDD aspect of BDD.
        \item
            Automating things, and continuous integration~\cite{ci} is an important
            aspect of BDD.
        \item
            BDD uses expectations instead of assertions
    \end{itemize}
\end{quote}

@@

Unfortunately, the type system of Haskell does not always guarantee
correct semantics.
For example, it does not ensure that division by zero does not occur.
Another example is lows of type classes. 
For instance, the {\tt Monad} class has three Monad lows 
that its instance \emph{should} satisfy
but
it is the programmers responsibility to ensure that
instance definitions \emph{behave} as \emph{expected}.

@@

\begin{itemize}
\item
    Implement Doctest in Haskell and add support for QuickCheck properties to Doctest (Section
    \ref{sec:for-users} and Section \ref{sec:doctest})
